::: {.chart-card}
[National unemployment, seasonally adjusted]{.chart-title}
```{r}
p_unrate <- ggplot(unrate_filtered, aes(x = date, y = unrate_percent)) +
  geom_line(color = LINE_COLOR, linewidth = 0.5) +
  geom_hline(yintercept = unrate_mean, linetype = "dotted",
             color = ANNOT_COLOR, linewidth = 0.6) +
  annotate("text", x = min(unrate_filtered$date, na.rm = TRUE), y = unrate_mean,
           label = paste0("Historic Average (", round(unrate_mean, 1), "%)"),
           hjust = 0, vjust = -0.7, size = 3, color = "#8c8c8c") +
  geom_vline(xintercept = ELECTION_DATE, linetype = "dashed", color = ELECTION_COLOR) +
  labs(x = NULL, y = "Percentage",
       caption = "Source: U.S. Bureau of Labor Statistics via FRED | Monthly") +
  theme_snapshot()
plotly_chart(p_unrate)
```

The national unemployment rate measures the share of the labor force that is
jobless and actively seeking work. The dotted line shows the period average.
:::

::: {.chart-card}
[Nonfarm private payroll employment]{.chart-title}
```{r}
adp |>
  line_chart(yvar = persons / 1e6, y_lab = "Persons (millions)",
             caption = "Source: Automatic Data Processing, Inc. via FRED | Monthly")
```

Total nonfarm private payroll employment tracks the number of paid workers
across all industries except government, farm, private household, and non-profit
employees.
:::

::: {.chart-card}
[Large-state continued unemployment claims]{.chart-title}
```{r}
p_large <- ggplot(group2_data, aes(x = date, y = unemployment_rate, color = state)) +
  geom_line() +
  geom_vline(xintercept = ELECTION_DATE, linetype = "dashed", color = ELECTION_COLOR) +
  scale_colour_manual(values = okabe_ito, name = NULL) +
  labs(x = NULL, y = "Continued claims rate (%)",
       caption = "Source: U.S. Bureau of Labor Statistics via FRED | Monthly average") +
  theme_snapshot()
plotly_chart(p_large)
```

Continued unemployment insurance claims as a percentage of each state's
civilian labor force, for the five largest states by population plus DC.
:::

::: {.chart-card}
[Total job openings (JOLTS)]{.chart-title}
```{r}
jolts_dat |>
  line_chart(yvar = value / 1000, y_lab = "Job openings (millions)",
             line_color = okabe_ito[2],
             caption = "Source: U.S. Bureau of Labor Statistics via FRED | Monthly")
```

Total job openings from the Bureau of Labor Statistics Job Openings and Labor
Turnover Survey (JOLTS), which counts all open positions at the end of each
reference month regardless of how they are advertised.
:::

::: {.chart-card}
[Initial jobless claims (4-week average)]{.chart-title}
```{r}
initial_claims_dat |>
  line_chart(yvar = value, y_lab = "Claims",
             caption = "Source: U.S. Employment and Training Administration via FRED | Weekly")
```

New claims for unemployment benefits, smoothed as a four-week moving average.
One of the timeliest labor-market signals — a sustained rise often flags
weakening before it shows up in the monthly unemployment rate.
:::

::: {.chart-card}
[Median wage growth]{.chart-title}
```{r}
wage_growth_dat |>
  line_chart(yvar = value, y_lab = "Percent",
             caption = "Source: Federal Reserve Bank of Atlanta via FRED | Monthly")
```

The Atlanta Fed's Wage Growth Tracker: the median year-over-year growth in
hourly wages for individuals, a three-month moving average. Because it follows
the same people over time, it is less distorted by shifts in who is employed.
:::
