::: {.chart-card}
[Top 10 countries for tourists visiting the US]{.chart-title}
```{r}
p_tourist <- ggplot(top_10_tourist_origins,
                    aes(x = date, y = total_visitors_100k, color = country)) +
  geom_line() +
  geom_vline(xintercept = ELECTION_DATE, linetype = "dashed", color = ELECTION_COLOR) +
  scale_colour_manual(values = rep(palette_10, length.out = 30), name = NULL) +
  labs(x = NULL, y = "Visitors (100k)",
       caption = "Source: International Trade Administration (I-94) | Monthly") +
  theme_snapshot()
plotly_chart(p_tourist)
```

Arrivals to the United States from the top 10 source countries, from I-94
border crossing data. Hover a line, or use the legend, to identify each country.
:::

::: {.chart-card}
[TSA checkpoint volume]{.chart-title}
```{r}
tsa_weekly |>
  line_chart(xvar = week_start, yvar = encounters_10k, y_lab = "Encounters (10k)",
             caption = "Source: Transportation Security Administration | Daily, aggregated weekly")
```

Passenger throughput at Transportation Security Administration checkpoints — a
direct read on how many people are moving through US airports, and a useful
proxy for both business and leisure travel demand.
:::

::: {.chart-card}
[Airline passenger load factor]{.chart-title}
```{r}
loadfactor_dat |>
  line_chart(yvar = value, y_lab = "Percent",
             caption = "Source: U.S. Bureau of Transportation Statistics via FRED | Monthly")
```

The share of available airline seats that are actually filled, across domestic
and international US carriers. Where TSA volumes show how many people are
flying, load factor shows how tightly airlines are matching capacity to that
demand — high values mean full planes and little slack.
:::
