::: {.chart-card}
[Light vehicle sales]{.chart-title}
```{r}
car_sales |>
  line_chart(yvar = value, y_lab = "Sales (millions)",
             caption = "Source: U.S. Bureau of Economic Analysis via FRED | Monthly",
             links = c(FRED = fred_url("TOTALSA")))
```

Total light vehicle sales in the United States at a seasonally adjusted annual
rate, including new domestic and imported cars and light trucks.
:::

::: {.chart-card}
[Consumer loans, all commercial banks]{.chart-title}
```{r}
consume_loans |>
  line_chart(yvar = value, y_lab = "USD (billions)",
             caption = "Source: Board of Governors of the Federal Reserve System via FRED | Weekly",
             links = c(FRED = fred_url("CLSACBW027SBOG")))
```

Outstanding consumer loan balances held by all commercial banks, including
credit card, auto, and personal loans but excluding mortgages. A broad measure
of household borrowing.
:::

::: {.chart-card}
[Consumer sentiment]{.chart-title}
```{r}
sentiment_dat |>
  line_chart(yvar = value, y_lab = "Index (1966 = 100)",
             caption = "Source: University of Michigan Survey of Consumers via FRED | Monthly",
             links = c(FRED = fred_url("UMCSENT")))
```

The University of Michigan Index of Consumer Sentiment measures household
attitudes toward personal finances, business conditions, and buying conditions,
benchmarked to 100 in 1966. Values above 100 reflect above-average confidence;
a sustained decline often precedes reduced consumer spending.
:::

::: {.chart-card}
[Regular gasoline price]{.chart-title}
```{r}
gas_dat |>
  line_chart(yvar = value, y_lab = "USD per gallon",
             caption = "Source: U.S. Energy Information Administration via FRED | Weekly",
             links = c(FRED = fred_url("GASREGW")))
```

The average US retail price for a gallon of regular gasoline. One of the most
visible prices households face — posted on every corner — and it tends to shape
how people feel about inflation more than the overall index does.
:::

::: {.chart-card}
[30-year fixed mortgage rate]{.chart-title}
```{r}
mortgage_dat |>
  line_chart(yvar = value, y_lab = "Percent",
             caption = "Source: Freddie Mac via FRED | Weekly",
             links = c(FRED = fred_url("MORTGAGE30US")))
```

The average rate on a 30-year fixed-rate mortgage. This is where market interest
rates reach households most directly: it sets the monthly payment on a home
purchase and largely determines who can afford to buy or refinance.
:::

::: {.chart-card}
[Rent of primary residence]{.chart-title}
```{r}
rent_dat |>
  line_chart(yvar = value, y_lab = "Index (1982-84 = 100)",
             caption = "Source: U.S. Bureau of Labor Statistics via FRED | Monthly",
             links = c(FRED = fred_url("CUSR0000SEHA")))
```

The rent component of the Consumer Price Index, averaged across US cities. Rent
is the single largest monthly cost for most renting households and one of the
slowest-moving parts of inflation, so it keeps pushing on the headline index
long after other prices have cooled.
:::

::: {.chart-card}
[Consumer Price Index (CPI-U)]{.chart-title}
```{r}
cpi_dat |>
  line_chart(yvar = value, y_lab = "Index (1982-84 = 100)",
             caption = "Source: U.S. Bureau of Labor Statistics via FRED | Monthly",
             links = c(FRED = fred_url("CPIAUCSL")))
```

The Consumer Price Index for All Urban Consumers (CPI-U) tracks changes in
average prices paid by urban consumers for a basket of goods and services,
benchmarked to 100 in the 1982-84 base period. The chart shows the level rather
than the year-over-year change.
:::

::: {.chart-card}
[Durable goods new orders]{.chart-title}
```{r}
durable_goods_dat |>
  line_chart(yvar = value, y_lab = "USD (millions)",
             caption = "Source: U.S. Census Bureau via FRED | Monthly",
             links = c(FRED = fred_url("DGORDER")))
```

New orders placed with domestic manufacturers for durable goods, items expected
to last three or more years such as aircraft, machinery, and electronics. A
leading indicator of manufacturing activity. One caveat when reading month to
month: the defense component is lumpy and contract-driven, so a single large
military order can swing the headline number without saying much about
underlying business investment. The series is seasonally adjusted.
:::
