::: {.chart-card}
[10-year Treasury yield]{.chart-title}
```{r}
bond_dat |>
  line_chart(yvar = value, y_lab = "Percent",
             caption = "Source: Board of Governors of the Federal Reserve System via FRED | Weekly average of daily")
```

The yield on 10-year U.S. Treasury securities at constant maturity, a benchmark
for long-term borrowing costs across the economy, including mortgage rates and
corporate bonds.
:::

::: {.chart-card}
[S&P 500 index]{.chart-title}
```{r}
spy_dat |>
  line_chart(yvar = value, y_lab = "Index",
             caption = "Source: S&P Dow Jones Indices LLC via FRED | Weekly average of daily")
```

The S&P 500 index tracks the market-capitalization-weighted performance of 500
large U.S. publicly traded companies, widely used as a proxy for the overall
U.S. equity market.
:::

::: {.chart-card}
[Housing starts]{.chart-title}
```{r}
house_dat |>
  line_chart(yvar = value, y_lab = "Thousands of units",
             caption = "Source: U.S. Census Bureau and U.S. Dept. of Housing and Urban Development via FRED | Monthly")
```

New privately-owned housing units started, at a seasonally adjusted annual rate.
Housing starts are a leading indicator of construction activity and broadly
reflect demand in the housing market.
:::

::: {.chart-card}
[Trade-weighted US dollar index]{.chart-title}
```{r}
usd_dat |>
  line_chart(yvar = value, y_lab = "Index",
             caption = "Source: Board of Governors of the Federal Reserve System via FRED | Weekly")
```

The value of the dollar against a basket of major trading partners' currencies,
weighted by trade volume. A stronger dollar makes imports cheaper and US exports
more expensive, and tends to weigh on the earnings of multinational firms.
:::

::: {.chart-card}
[GDP nowcast (Atlanta Fed)]{.chart-title}
```{r}
gdpnow_dat |>
  line_chart(yvar = value, y_lab = "Percent (annualized)",
             caption = "Source: Federal Reserve Bank of Atlanta via FRED | Quarterly")
```

GDPNow is the Atlanta Fed's running estimate of real GDP growth for the current
quarter, rebuilt as each new piece of source data arrives. It is a nowcast, not
an official statistic — it fills the gap before the Bureau of Economic Analysis
publishes its first estimate.
:::
