::: {.chart-card}
[National unemployment, seasonally adjusted]{.chart-title}
```{r}
p_unrate <- ggplot(unrate_filtered, aes(x = date, y = unrate_percent)) +
  geom_line(color = LINE_COLOR, linewidth = 0.5) +
  geom_hline(yintercept = unrate_mean, linetype = "dotted",
             color = ANNOT_COLOR, linewidth = 0.6) +
  geom_vline(xintercept = ELECTION_DATE, linetype = "dashed", color = ELECTION_COLOR) +
  labs(x = NULL, y = "Percentage",
       caption = "Source: U.S. Bureau of Labor Statistics via FRED | Monthly") +
  theme_snapshot()

# The label for the dotted mean line is a plotly annotation rather than a
# ggplot annotate(): anchored to the left edge of the plotting area in PAPER
# coordinates (x = 0, xanchor = "left") it sits at the same place but can never
# overflow the panel, so it stays fully visible at any window or chart width.
# Only y is in data coordinates, so it tracks the line it labels.
plotly_chart(
  p_unrate,
  links = c(FRED = fred_url("UNRATE")),
  annotations = list(list(
    text = sprintf("Period average (%.1f%%)", unrate_mean),
    xref = "paper", x = 0, xanchor = "left",
    yref = "y", y = unrate_mean, yanchor = "bottom", yshift = 3,
    showarrow = FALSE, font = list(size = 10, color = "#8c8c8c"))))
```

The national unemployment rate measures the share of the labor force that is
jobless and actively seeking work. The dotted line is the average across the
period charted here (`r format(min(unrate_filtered$date), "%B %Y")` to
`r format(max(unrate_filtered$date), "%B %Y")`) &mdash; the mean of every
monthly reading shown, not a long-run historical average. It does not change
when you switch the 1Y / 2Y / All window.
:::

::: {.chart-card}
[Nonfarm private payroll employment]{.chart-title}
```{r}
adp |>
  line_chart(yvar = persons / 1e6, y_lab = "Persons (millions)",
             caption = "Source: Automatic Data Processing, Inc. via FRED | Monthly",
             links = c(FRED = fred_url("ADPWNUSNERSA")))
```

Total nonfarm private payroll employment tracks the number of paid workers
across all industries except government, farm, private household, and non-profit
employees.
:::

::: {.chart-card}
[Large-state continued unemployment claims]{.chart-title}
```{r}
p_large <- ggplot(group2_data, aes(x = date, y = unemployment_rate, color = state)) +
  geom_line() +
  geom_vline(xintercept = ELECTION_DATE, linetype = "dashed", color = ELECTION_COLOR) +
  scale_colour_manual(values = okabe_ito, name = NULL) +
  labs(x = NULL, y = "Continued claims rate (%)",
       caption = paste("Source: state continued claims via FRED;",
                       "labor force from the U.S. Bureau of Labor Statistics",
                       "| Monthly average")) +
  theme_snapshot()
# Two sources here: FRED supplies the weekly claims (numerator), BLS the state
# civilian labor force (denominator), so the note links to both.
plotly_chart(p_large, links = c(
  FRED = "https://fred.stlouisfed.org/release/tables?rid=469&eid=1192108#snid=1192113",
  "U.S. Bureau of Labor Statistics" = "https://www.bls.gov/news.release/laus.t01.htm"))
```

Continued unemployment insurance claims as a percentage of each state's
civilian labor force, for the five largest states by population plus DC.
:::

::: {.chart-card}
[Total job openings (JOLTS)]{.chart-title}
```{r}
jolts_dat |>
  line_chart(yvar = value / 1000, y_lab = "Job openings (millions)",
             line_color = okabe_ito[2],
             caption = "Source: U.S. Bureau of Labor Statistics via FRED | Monthly",
             links = c(FRED = fred_url("JTSJOL")))
```

Total job openings from the Bureau of Labor Statistics Job Openings and Labor
Turnover Survey (JOLTS), which counts all open positions at the end of each
reference month regardless of how they are advertised.
:::

::: {.chart-card}
[Initial jobless claims (4-week average)]{.chart-title}
```{r}
initial_claims_dat |>
  line_chart(yvar = value, y_lab = "Claims",
             caption = "Source: U.S. Employment and Training Administration via FRED | Weekly",
             links = c(FRED = fred_url("IC4WSA")))
```

New claims for unemployment benefits, smoothed as a four-week moving average.
One of the timeliest labor-market signals — a sustained rise often flags
weakening before it shows up in the monthly unemployment rate.
:::

::: {.chart-card}
[Median wage growth]{.chart-title}
```{r}
wage_growth_dat |>
  line_chart(yvar = value, y_lab = "Percent",
             caption = "Source: Federal Reserve Bank of Atlanta via FRED | Monthly",
             links = c(FRED = fred_url("FRBATLWGT3MMAWMHWGO")))
```

The Atlanta Fed's Wage Growth Tracker: the median year-over-year growth in
hourly wages for individuals, a three-month moving average. Because it follows
the same people over time, it is less distorted by shifts in who is employed.
:::
